Make any stupid plot you want

### 2020-12-23 draft/sections/math.tex
further down the defining types in P rabbit hole

The visual fiber bundle ($V$, $K$, $\pi$, $P$) has section $\mu: V \rightarrow K$ that resolves to a visual variable $\mu$ \cite{bertinIIPropertiesGraphic2011,munznerMarksChannels} in fiber $P$. The space of visual variables types in $P$ is restricted to the types $Q$ takes as input.

\subsubsection{Example} 
Given a  $Q$ that manufactored lines with signature $Q(\mu_{xpos}, \mu_{ypos}, \mu_{width}, \mu_{color}, \mu_{style})$ then the $P=\Gamma(\mu)$ for this line artist would be:
\begin{itemize}
    \item $C = \{\text{xpos, ypos, width, color, style}\}$ 
    \item $DT =\{\mathbb{R}, \mathbb{R}, \mathbb{R}, \mathbb{R}^3, f:s\mapsto\mathbb{R}^3 \}$ 
    \item $P = U \times_{DT} C$
\end{itemize}

>>>>

The visual fiber bundle ($V$, $K$, $\pi$, $P$) has section $\mu: V \rightarrow K$ that resolves to a visual variable $\mu$ \cite{bertinIIPropertiesGraphic2011,munznerMarksChannels} in fiber $P$. The space of visual variables types in $P$ is restricted to the types $Q$ takes as input. 
\subsubsection{Retinal Variables}
Visual Variables need to ultimately target some aspect of D

\subsubsection{Example} 
Given a $Q$ with signature $Q(\mu_{xpos}, \mu_{ypos}, \mu_{width}, \mu_{color}, \mu_{style})$ then the $P=\Gamma(\mu)$ for this artist would be:
\begin{itemize}
    \item $C = \{\text{xpos, ypos, width, color, style}\}$ 
    \item $DT =\{\mathbb{R}, \mathbb{R}, \mathbb{R}, \mathbb{R}^3, f:s\mapsto\mathbb{R}^3 \}$ 
    \item $P = U \times_{DT} C$
\end{itemize}
